% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
\pdfpagewidth=8.5in 
\pdfpageheight=11in
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\name{Andrew D'Angelo\\[12pt]} % the \\[12pt] adds a blank line after name
\address{
  {\bf Present Address} \\ 4000 NE 15th Avenue \\ Seattle, WA 98195 \\
  {\bf Permanent Address} \\ 1310 Maple Avenue \\ Wilmette, IL 60091 }
\address{
  {\bf Contact Information} \\ dangeloandrew@outlook.com \\ +1 (847) 906-3448 \\
  {\bf GitHub Profile} \\ https://github.com/excelangue }

\begin{resume}

\section{Summary}
A dedicated and creative student with a strong mathematical background who wants to leverage both self-taught and formal experience designing and writing computer software. Able to design architectures and algorithms at a high level and then implement solutions at a lower level in any of a multitude of languages and frameworks.

\section{Education}

{\bf Undergraduate,} University of Washington, Seattle, WA \hfill 2014\textendash Present
\begin{itemize} \itemsep -2pt  % reduce space between items
\item Currently a junior studying Computer Science and Applied Mathematics
\item 2014\textendash 2015 school year: Dean's List with 3.8 GPA
%\item Nominated twice for the Soceity for Collegiate Leadership \& Achievement soceity
\end{itemize}

{\bf Student,}  New Trier High School, Winnetka, IL \hfill 2010\textendash 2014
\begin{itemize} \itemsep -2pt  % reduce space between items
\item 4.4 weighted GPA, 36 ACT
\item Presidential Scholar semifinalist
\item Member of the German National Honor Society
\end{itemize}

% Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
\section{Computer \\ Skills}
  \begin{tabular}{l p{3in}}
    \underline{Software:} & Windows, Windows Server 2012, OS X, Linux system administration, primarily Arch and Debian \\
    \underline{Languages:} & C for PC and Game Boy Advance, Python with Django and Web2Py, Java, C\# and F\# for the .NET framework, LISP. Current focus on machine learning and biological simulation in F\#
 \end{tabular}

\section{Work \\ Experience}

{\bf Software Engineering Intern,} Quicket Solutions, Champaign, IL \hfill Summer 2015
\begin{itemize} \itemsep -2pt  % reduce space between items
\item Wrote and maintained database interface and backend management Python and Web2Py code creating a complete electronic police citation management service.
\item Experienced designing and implementing software solutions in a tight-knit, collaborative group and planning extensible and robust systems for data processing in a fast moving startup environment.
\end{itemize}

{\bf Technical Consultant,} Panorama Innovation, Wilmette, IL \hfill Jun. 2014\textendash Sept. 2014
\begin{itemize} \itemsep -2pt  % reduce space between items
\item Research, system design \& software implementation for retail intelligence systems using OpenWRT on commodity access points for data collection and Python for data processing and analytics.
\end{itemize}

{\bf IT Technician,} Unite Here Health, Chicago, IL \hfill Jul. 2014\textendash Aug. 2014
\begin{itemize} \itemsep -2pt  % reduce space between items
\item Computer system set-up and maintenance for health insurance events. Responsibilities included wired and wireless network configuration, cabling, Windows networking, and troubleshooting.
\end{itemize}

{\bf Published two apps to the Windows Phone store} \hfill May 2014
\begin{itemize} \itemsep -2pt  % reduce space between items
\item \underline{Thorntons++}: a customer loyalty and coupon app for a gas station chain.
\item \underline{Omeddle}: an Omegle chat client with the additional ability to intercept and modify messages sent between other Omegle users. Peaked at 2,000 downloads a month, won 3rd place at the 2014 Microsoft //publish/ event in the Chicago app competition.
\end{itemize}

\end{resume}
\end{document}



